A compact program for 3D passive seismic \\ source-location imaging

### 2021-05-12 passive/paper.tex
add passive

\address{
%\footnotemark[1]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%chenyk2016@gmail.com\\
%%yangkang.chen@zju.edu.cn \\
%\footnotemark[2]
%ENSN Lab \\
%Seismology Department \\
%National Research Institute of Astronomy and Geophysics (NRIAG)\\
%Helwan 11731, Egypt\\
%engomar91@ gmail.com\\
%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[4]
%College of Geology and Environment\\
%Xi’an University of Science and Technology\\
%Xi’an, Shaanxi Province, China, 710054 \\
%lwxwyh506673@126.com\\
%\footnotemark[5]Bureau of Economic Geology \\
%John A. and Katherine G. Jackson School of Geosciences \\
%The University of Texas at Austin \\
%University Station, Box X \\
%Austin, TX 78713-8924 \\
%sergey.fomel@beg.utexas.edu\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

%\lefthead{Liu et al.}
\righthead{3D passive imaging\\
Declaration of Competing Interests: The authors acknowledge there are no conflicts of interest recorded.}

@@

\clearpage
Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
%yangkang.chen@zju.edu.cn \\
\footnotemark[2]
ENSN Lab \\
Seismology Department \\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt\\
engomar91@ gmail.com\\
\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[4]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
\footnotemark[5]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\

>>>>

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com\\
%yangkang.chen@zju.edu.cn \\
\footnotemark[2]
ENSN Lab \\
Seismology Department \\
National Research Institute of Astronomy and Geophysics (NRIAG)\\
Helwan 11731, Egypt\\
engomar91@ gmail.com\\
\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
Yangtze University\\
Daxue Road No.111\\
Caidian District\\
Wuhan, China, 430100 \\
\footnotemark[4]
College of Geology and Environment\\
Xi’an University of Science and Technology\\
Xi’an, Shaanxi Province, China, 710054 \\
lwxwyh506673@126.com\\
\footnotemark[5]Bureau of Economic Geology \\
John A. and Katherine G. Jackson School of Geosciences \\
The University of Texas at Austin \\
University Station, Box X \\
Austin, TX 78713-8924 \\
sergey.fomel@beg.utexas.edu\\
Corresponding Author: Yangkang Chen (chenyk2016@gmail.com) 
}

%\lefthead{Liu et al.}
%\righthead{3D passive imaging\\
%Declaration of Competing Interests: The authors acknowledge there are no conflicts of interest recorded.}

@@

%\clearpage
%Yangkang Chen\footnotemark[1], Omar M. Saad\footnotemark[1]\footnotemark[2], Min Bai\footnotemark[3],  Xingye Liu\footnotemark[4], Sergey Fomel\footnotemark[5]  \\
%\footnotemark[1]
%School of Earth Sciences\\
%Zhejiang University\\
%Hangzhou, Zhejiang Province, China, 310027\\
%chenyk2016@gmail.com\\
%%yangkang.chen@zju.edu.cn \\
%\footnotemark[2]
%ENSN Lab \\
%Seismology Department \\
%National Research Institute of Astronomy and Geophysics (NRIAG)\\
%Helwan 11731, Egypt\\
%engomar91@ gmail.com\\
%\footnotemark[3] Key Laboratory of Exploration Technology for Oil and Gas Resources of Ministry of Education\\
%Yangtze University\\
%Daxue Road No.111\\
%Caidian District\\
%Wuhan, China, 430100 \\
%\footnotemark[4]
%College of Geology and Environment\\
%Xi’an University of Science and Technology\\
%Xi’an, Shaanxi Province, China, 710054 \\
%lwxwyh506673@126.com\\
%\footnotemark[5]Bureau of Economic Geology \\
%John A. and Katherine G. Jackson School of Geosciences \\
%The University of Texas at Austin \\
%University Station, Box X \\
%Austin, TX 78713-8924 \\
%sergey.fomel@beg.utexas.edu\\
%
